---
title: "STAT 1261: Principles of Data Science"
subtitle: "Assignment 1: R and RStudio" 
output:
  html_document:
    fig_height: 5
    fig_width: 7
  pdf_document:
    fig_height: 5
    fig_width: 7
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r, setup, include=FALSE}
library(mdsr)   # Load additional packages here 
library(tidyr)
library(tm)
library(wordcloud)


# Some customization.  You can alter or delete as desired (if you know what you are doing).
trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```


## Instruction
Due day: Friday, Sep. 7, 2018

First read Appendix B of the textbook **Modern Data Science with R**: 

Make sure you include necessary R code to show your work.

Total points: 50


## 1. Objects 
A user has typed the following commands into the console. 

#### 1) Show the value of each object and use R command to measure the length of them. (8 points)

```{r}
obj1 <- 2:10
obj2 <- c(2, 5)
obj3 <- c(TRUE, FALSE)
obj4 <- 42
```

#### 2) What values are returned by the following commands? (9 points)

```{r eval=FALSE}
obj1 * 10
obj1[2:4]
obj1[-3]
obj1 + obj2
obj1 * obj3
obj1 + obj4
obj2 + obj3
sum(obj2)
sum(obj3)
```

## 2. Vectors 
A user has typed the following commands into the console.

```{r}
a <- c(10, 15)
b <- c(TRUE, FALSE)
c <- c("happy", "sad")
```

What do each of the following commands return? (5 points)

```{r,eval = FALSE}
a+b
a*b
a+c
d <- c(a,b);d
e <- c(a,c);e
```
## 3. Errors 
For each of the following assignment statements, describe the error (or note why it does not generate an error).(5 points)

```{r, eval=FALSE}
result1 <- sqrt 10
result2 <-- "Hello to you!"
3result <- "Hello to you"
result4 <- "Hello to you
result5 <- date()
```
## 4. Matrices

#### 1) Create a matrix as follows by writing code (10 points)
```{r,echo = FALSE}
a <- seq(2,18,2)
M1 <- matrix(a,3,3)
print(M1)
M2 <- matrix(a,3,3,byrow=TRUE)
print(M2)
```
#### 2) Pull out the value at the 2nd row and 3rd column of M1 using R (2 points)

#### 3) Pull out the value at the 3rd row and 2nd column of M2 using R (2 points)

#### 4) Pull out the values in the 1st row in M1 using R (2 points)

#### 5) Pull out the values in the 1st column in M2 using R (2 points)

## 5.Calculate the following using R (5 points)
#### 1) $e^{-2}$ + $e^{2}$
#### 2) $sin(\pi/3)$+cos$(\pi/4)$
#### 3) Round down the result of 2) to the nearest integer
#### 4) Round up the result of 1) to the nearest integer
#### 5) Calculate the remainder of $967/25$ using R
